Deep Reinforcement Learning for Conservation Decisions

### 2022-06-02 manuscript/manuscript.Rmd

We provide two examples that illustrate the application and potential of deep RL to ecological and conservation problems, highlighting both the potential and the inherent challenges.
Annotated code for these examples may be found in Appendix B and at <https://github.com/boettiger-lab/rl-intro>.

>>>>

We provide two examples that illustrate the application and potential of deep RL to ecological and conservation problems, highlighting both the potential and the inherent challenges.
Annotated code for these examples may be found in Appendix B and at <https://github.com/boettiger-lab/rl-intro>.
All algorithms were run on an NVIDIA Quadro RTX 8000 GPU.
The training  budget for the fishing scenario was 300K timesteps (3K runs, taking about 25 minutes).
The training budget for the tipping point example was 3M timesteps (6K runs, taking around 3 hours).
Software details and hyperparameters are provided in the associated GitHub repo.
Hyperparameter tuning typically required 100s of training runs using both Optuna, a python-based hyperparameter optimization module, and manual adjustments.
